Lens Modeling in \sw

### 2013-09-09 text/tex/results.tex
edits

\section{Results} \label{sec:results}

>>>>

\section{The lens modelling challenge} \label{sec:results}

\subsection{\sw} \label{sec:SpaceWarps}
some words about \sw

\subsection{The simulated lenses} \label{sec:sims}

In order to estimate users performance, \sw included some simulated lensing configurations in their image set.

There are three kinds of simulated lenses.

Sims produced using {\tt gravlens}
\citep{2001astro.ph..2341K,2001astro.ph..2340K}.

\begin{itemize}
  \item {\em Quasar:\/} A singular elliptical isothermal plus constant
    external shear, with a circular Gaussian source.
  \item {\em Galaxy:\/} Lens as with quasar, but elliptical de
    Vaucouleurs source.
  \item {\em Galaxy:\/} Lens is circular NFW plus one dominant
    elliptical SIE and perturbating elliptical SIEs, source as with
    galaxy.
\end{itemize}

Singular isothermal is in equations (33-35) of
\cite{2001astro.ph..2341K} with core radius set to zero. NFW is
equations (48,50) of the same paper, and shear is the $\gamma$ term in
equation (76) of that work.

\subsection{The Test setup} \label{sec:testsetup}
We made use of this simulated lenses and further tested the volunteers abilities to model those simulated lensing images.

The testing was done with a small number of volunteers ($N_v=4$) and a set of simulated configurations ($N_{sim}=29$) chosen to represent some typical configurations.

Two tests were done on the models created by the volunteers:

\begin{enumerate}
  \item Correct identification of extremal points
  \item Reproduction of the mass distribution of the lens
\end{enumerate}

The first test required the volunteers to accomplish 2 tasks: First to identify and distinguish lensed images from background light sources.
Second to come up with a logical ordering of the arrival time of those lensed images.
It also tries to identify the problems volunteers encounter during modelling.

The second test compared the enclosed mass $\kappa(r)$ of the models and the simulations.

### 2013-09-09 text/tex/spaghetti.tex
edits

\section {Setup} \label{sec:setup}

\subsection{\sw} \label{sec:SpaceWarps}
some words about \sw

\begin{figure}
  \centering
  \subfigure{\includegraphics[width=0.45\textwidth]{fig/sims/006941/input.png}}
  \subfigure{\includegraphics[width=0.45\textwidth]{fig/sims/007022/input.png}}
  \subfigure{\includegraphics[width=0.45\textwidth]{fig/sims/006919/input.png}}
%  \includegraphics[width=.45\textsize]{fig/spag6941.png}
%  \includegraphics[width=.45\textsize]{fig/spag7022.png}
%  \includegraphics[width=.45\textsize]{fig/spag6919.png}
  \caption{Examples of Spaghetti input.  The models from these appear
    later in Figures \ref{fig:6941}, \ref{fig:7022} and \ref{fig:6919}.
  \label{fig:input-spag}}
\end{figure}

@@

\subsection{The simulated lenses} \label{sec:sims}

In order to estimate users performance, \sw included some simulated lensing configurations in their image set.

There are three kinds of simulated lenses:

\begin{itemize}
  \item {\em Quasar:\/} A singular elliptical isothermal plus constant
    external shear, with a circular Gaussian source.
  \item {\em Galaxy:\/} Lens as with quasar, but elliptical de
    Vaucouleurs source.
  \item {\em Galaxy:\/} Lens is circular NFW plus one dominant
    elliptical SIE and perturbating elliptical SIEs, source as with
    galaxy.
\end{itemize}
Lenses follow \cite{2001astro.ph..2341K,2001astro.ph..2340K}.

Parameters can be looked up in online supplement.

\subsection{The Test setup} \label{sec:testsetup}
We made use of this simulated lenses and further tested the volunteers abilities to model those simulated lensing images.

The testing was done with a small number of volunteers ($N_v=4$) and a set of simulated configurations ($N_{sim}=29$) chosen to represent some typical configurations.

Two tests were done on the models created by the volunteers:

\begin{enumerate}
  \item Correct identification of extremal points
  \item Reproduction of the mass distribution of the lens
\end{enumerate}

The first test required the volunteers to accomplish 2 tasks: First to identify and distinguish lensed images from background light sources.
Second to come up with a logical ordering of the arrival time of those lensed images.
It also tries to identify the problems volunteers encounter during modelling.

The second test compared the enclosed mass $\kappa(r)$ of the models and the simulations.

>>>>

\begin{figure}
  \centering
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/sims/006941/input.png}} \\
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/sims/007022/input.png}} \\
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/sims/006919/input.png}}
  \caption{Examples of Spaghetti input.  The models from these appear
    later in Figures \ref{fig:6941}, \ref{fig:7022} and \ref{fig:6919}.
  \label{fig:input-spag}}
\end{figure}

@@
